---
title: "Assignment_03_ML"
author: "Yash"
date: "2022-10-19"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Installing Required packages and loading the dataset.
```{r }
#install.packages("tidyverse")
library(tidyverse)
#install.packages("reshape")
library(reshape)
#install.packages("caret")
library(caret)
#install.packages("e1071")
library(e1071)
Ub <- read_csv("C:/Users/YASH/Downloads/UniversalBank.csv")
head(Ub)
tail(Ub)
colnames(Ub)

```
#Transforming data into factors (categorical).

```{r}
Ub$Personal.Loan = as.factor(Ub$Personal.Loan)
Ub$Online = as.factor(Ub$Online)
Ub$CreditCard = as.factor(Ub$CreditCard) 

```
#Partitioning the 60% of data in training set and remaining into validation set
```{r}
set.seed(456)
ub.train.data <- sample(row.names(Ub), 0.6*dim(Ub)[1]) # 60 % training
ub.valid.data <- setdiff(row.names(Ub), ub.train.data) # 40 % validation
ub.train <- Ub[ub.train.data, ] # assigning the ub.train.data into data frame
ub.valid <- Ub[ub.valid.data, ] # assigning the validation index into data frame
train <- Ub[ub.train.data, ] # Duplicating the data frame ub.train
valid = Ub[ub.train.data,] # Duplicating the data frame ub.valid

```

#A. Create a pivot table for the training data with Online as a column variable, CC as a row variable, and Loan as a secondary row variable. The values inside the table should convey the count. In R use functions melt() and cast(), or function table().

Pivot table
```{r}
#install.packages("reshape2")
library(reshape2)
melt = melt(train,id=c("CreditCard","Personal.Loan"),variable= "Online")
cast = dcast(melt,CreditCard+Personal.Loan~Online) # dcast is the process of turning online, personal loan, and credit card data into pivot tables.
cast[,c(1,2,3,14)] # Casting column number 14: Personal loan, ID, and credit card, respectively

```

#B. Consider the task of classifying a customer who owns a bank credit card and is actively using online banking services. Looking at the pivot table, what is the probability that this customer will accept the loan offer? [This is the probability of loan acceptance (Loan = 1) conditional on having a bank credit card (CC = 1) and being an active user of online banking services (Online = 1)].
```{r}
Ub.Loan.CC1 <- 77/3000 #According to the pivot table, the value for Loan is 77, and the value for CC is 1. and 3000 is the total of 1924 + 198 + 801 + 77 = 3000.
Ub.Loan.CC1 # which is 26 %.

```
#C. Create two separate pivot tables for the training data. One will have Loan (rows) as a function of Online (columns) and the other will have Loan (rows) as a function of CC.
```{r}
melt1 = melt(train,id=c("Personal.Loan"),variable = "Online") # Melting Personal loan and Online data into pivot table
melt2 = melt(train,id=c("CreditCard"),variable = "Online") # CREDIT CARD DATA MELTING WITH REFERENCE TO ONLINE
cast1 =dcast(melt1,Personal.Loan~Online) # Casting Personal loan and online values
cast2=dcast(melt2,CreditCard~Online) # Casting Personal loan and online values
Ub.Loanonline=cast1[,c(1,13)]
Ub.LoanCC = cast2[,c(1,14)]
Ub.Loanonline #shows the number of personal loans in reference to online
Ub.LoanCC # shows the number of credit cards in reference to internet.

```
D. Compute the following quantities [P (A | B) means “the probability of A given B”]:
1.P (CC = 1 | Loan = 1) (the proportion of credit card holders among the loan acceptors)
2.P(Online=1|Loan=1)
3.P (Loan = 1) (the proportion of loan acceptors)
4.P(CC=1|Loan=0)
5.P(Online=1|Loan=0)
6.P(Loan=0)

```{r}
table(train[,c(14,10)])   # creating a pivot table with the columns 14 and 10 representing personal loans and credit cards from training
table(train[,c(13,10)])   # Creating a pivot table for column 13 and 10 which is online and personal loan from training
table(train[,c(10)])     # Personal loan pivot table There are 2725 and 275 from training, respectively.

```
1. P(CC = 1 | Loan = 1)
```{r}
Ub.CCUb.Loan1 = 77/(77+198)   # We can obtain the CC= 1 and Loan = 1 values by referring to the above pivot table, which is 77 divided by CC = 0 and PL 1 198.
Ub.CCUb.Loan1


```

2. P(Online=1|Loan=1)
```{r}
Ub.ONUb.Loan1 =166/(166+109) # We can get the online = 1 and loan = 1 values from the pivot table above.
Ub.ONUb.Loan1

```
3. P(Loan = 1)
```{r}
Ub.Loan1 =275/(275+2725) # By referring the above pivot table we can get the Loan = 1
Ub.Loan1

```
4. P(CC=1|Loan=0)
```{r}
Ub.CCLoan.01= 801/(801+1924) #Using the pivot table above, we can obtain the CC = 1 and Loan = 0 values / CC 0 and PL 0 values.
Ub.CCLoan.01

```
5. P(Online=1|Loan=0)
```{r}
UB.ON1.L0= 1588/(1588+1137) # We can get the online = 1 and loan = 0 values from the pivot table above.
UB.ON1.L0


```
6. P(Loan=0)
```{r}
Ub.Loan0= 2725/(2725+275) # We can obtain the Loan = 0 values by  the pivot table above.
Ub.Loan0

```

E. Use the quantities computed above to compute the naive Ba1 probability P(Loan = 1 | CC = 1, Online = 1).
```{r}
ub.Naivebayes = ((77/(77+198))*(166/(166+109))*(275/(275+2725)))/(((77/(77+198))*(166/(166+109))*(275/(275+2725)))+((801/(801+1924))*(1588/(1588+1137))*2725/(2725+275)))
ub.Naivebayes # ~91 % is the probability


```

F. Compare this value with the one obtained from the pivot table in (b). Which is a more accurate estimate? 9.05% are very similar to the 9.7% the difference between the exact method and the naive-baise method is the exact method would need the the exact same independent variable classifications to predict, where the naive bayes method does not.

```{r}
library(caret)
library(e1071)
ub.nb.train = ub.train[,c(10,13,14)] # Personal loan, credit card, and online column training dataub.nb.test =ub.valid[,c(10,13,14)] # testing set data from the same columns.
ub.naivebayes.1 = naiveBayes(Personal.Loan~.,data=ub.nb.train) #Using the naivebayes algorithm to personal loan and training data.
ub.naivebayes.1

```

